### 2015-09-06 manuscript/content/eval.tex
Final data.

So how does this do as a regression problem? We first considered the most basic: a linear regression model. This did not perform well at all. We next trained a neural network (ANN) model on the data. \begin{figure}
	\includegraphics[width=1.0\textwidth]{../figs/nn_all}
	\caption{ANN predictions (blue) over actual BAC (black, jitterred) using test data.}
	\label{fig:nn_all}
\end{figure}This was even slower than the SVM which forced us to subsample to 8\% of the original data. The best performing ANN had a structure with two hidden layers of five nodes each. Figure \ref{fig:nn_all} plots the BAC predictions in of the neural network model on top of the actual values from the test set. The real values are jittered to give a sense of the density of the test data, the prediction values in blue are not. This model acheived a R$^2$ value of 0.525, with RMSE of 0.026. Much better than the linear regression model, but not nearly as good as the classification models.

>>>>

So how does this do as a regression problem? We first considered the most basic: a linear regression model. This did not perform well at all. We next trained a neural network (ANN) model on the data. \begin{figure}
	\includegraphics[width=1.0\textwidth]{../figs/nn_all}
	\caption{ANN predictions (blue) with actual BAC data (black) on test partition.}
	\label{fig:nn_all}
\end{figure}The best performing ANN had a structure with twenty nodes in one hidden layer. This was determined by doubling and then reducing node count to find the best performance. Additional layers did not show any improvement (the 'neuralnet' package was used to test multiple layers). Figure \ref{fig:nn_all} plots the BAC predictions of the ANN along with the actual values using data from a test partition. The ANN model achieved a R$^2$ value of 0.524 $\pm$ 0.015, with RMSE of 0.026 $\pm$ 0.000. It performed much better than the linear regression model, but not nearly as good as the classification models.

### 2015-09-06 manuscript/content/method.tex
CV log. and SVM_1
Final data.

The heart rate increases over time for three of the subjects (0, 2, 3) at different rates, decreases for one (4), and stays level for one (1). These observations are consistent with data in \cite{Assaad:2006}; a study where the authors relate low and high HR responses to behavioral traits. Interestingly, most of the subjects seem to show two patterns of HR activity. One is the baseline HR activity, and another is an excitied HR activity that seems to have better correlation with BAC. This is most clearly seen in the plot for subject 0, shown in Figure \ref{fig:heart_rate_split}. It's not a consistent pattern, however. Subject 1 had a very level heart rate with spikes at the regular drinking intervals, and subject 2 had relatively little variance throughout. Overall, it seems that experiencing excitement while intoxicated results in a more exaggerated HR response than while sober. This may be useful information for determining drunkenness.

\begin{figure}
	\includegraphics[width=1.0\textwidth]{../figs/heart_rate_split}
	\caption{Heart rate split into baseline and excited states.}
	\label{fig:heart_rate_split}
\end{figure}

Next, we plotted the normalized skin temperature over time on top of the normalized BAC values; this is shown in Figure \ref{fig:skin_temperatures}. Visually, we see that the correlation of skin temperature and BAC is highly significant. This is because of the well known vasodilation effect of alcohol causing warm blood to come near the surface of the skin \cite{Dekker:1999}. It is also known that with a high enough level of intoxication it behaves as a vasoconstrictor and drops skin temperature, which we see with subjects 4 and 5 who had reached the highest BAC of the group. Subject 2 had a rapid decrease in temperature at the beginning (we may have started collection too soon before the smartwatch sensor adjusted to his skin temperature), it may be appropriate to discard this portion.

\begin{figure}
	\includegraphics[width=1.0\textwidth]{../figs/skin_temperatures}
	\caption{Skin Temperature and BAC per subject (normalized).}
	\label{fig:skin_temperatures}
\end{figure}

@@

All work will be performed in R version 3.2.1 using the additional 'neuralnet' and 'kernlab' packages. Any necessary additional information will be provided in the evaluation section.

>>>>

The heart rate increases over time for three of the subjects (0, 2, 3) at different rates, decreases for one (4), and stays level for one (1). These observations are consistent with data in \cite{Assaad:2006}; a study where the authors relate low and high HR responses to behavioral traits. Interestingly, most of the subjects seem to show two patterns of HR activity. One is the baseline HR activity, and another is an excitied HR activity that seems to have better correlation with BAC. This is most clearly seen in the plot for subject 0, shown in Figure \ref{fig:heart_rate_split}. \begin{figure}
	\includegraphics[width=1.0\textwidth]{../figs/heart_rate_split}
	\caption{Heart rate split into baseline and excited states.}
	\label{fig:heart_rate_split}
\end{figure}It's not a consistent pattern, however. Subject 1 had a very level heart rate with spikes at the regular drinking intervals, and subject 2 had relatively little variance throughout. Overall, it seems that experiencing excitement while intoxicated results in a more exaggerated HR response than while sober. This may be useful information for determining drunkenness.

Next, we plotted the normalized skin temperature over time on top of the normalized BAC values; this is shown in Figure \ref{fig:skin_temperatures}. \begin{figure}
	\includegraphics[width=1.0\textwidth]{../figs/skin_temperatures}
	\caption{Skin Temperature and BAC per subject (normalized).}
	\label{fig:skin_temperatures}
\end{figure}Visually, we see that the correlation of skin temperature and BAC is highly significant. This is because of the well known vasodilation effect of alcohol causing warm blood to come near the surface of the skin \cite{Dekker:1999}. It is also known that with a high enough level of intoxication it behaves as a vasoconstrictor and drops skin temperature, which we see with subjects 4 and 5 who had reached the highest BAC of the group. Subject 2 had a rapid decrease in temperature at the beginning (we may have started collection too soon before the smartwatch sensor adjusted to his skin temperature), it may be appropriate to discard this portion.

@@

All work will be performed in R version 3.2.1 using the additional 'nnet' and 'kernlab' packages. Any necessary additional information will be provided in the evaluation section.
